Perceptual symbol grounding in \\Holographic memories

### 2016-11-08 papers/hrr-paper/paper.tex
Clean up .bib file and filter entries for minimal display
Improved plots, added values for probing bar chart (still require processing)

>>>>

	FOR BAR CHART:

	Probe at (19,-26.75):

	[('keys', 0.22827929349034107), ('Watch', -0.018549398363469777), ('mug', -0.025309361445942102), ('wallet', -0.034187368731921304), ('pen', 0.2098596398998358), ('mouse', -0.023035819302988644)]

	Probe at (-13,21.5):

[('keys', -0.020032173214673016), ('Watch', -0.034034204029029354), ('mug', 0.03443254630997427), ('wallet', 0.16100011074269183), ('pen', 0.089801145874187763), ('mouse', -0.027742071303527464)]
